### 2021-09-08 manuscript/synthetic_data.tex
replace bad non-ASCII character by "-"

The  three rows in Figure \ref{fig:synthetic_data_comparison_v2} show the flight patterns of the simulated airborne magnetic surveys (the upper row), the noise-corrupted total-field anomalies (the middle row) calculated over the flight patterns, and the true upward-continued total-field anomalies at $z = −1, \, 300$ m (the lower row).

@@

We performed the upward continuations of the noise-corrupted total-field anomalies 
(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method (equation \ref{eq:estimated-p-parameter-space}), 
the convolutional equivalent layer (our method), and 
the classical approach in the Fourier domain.
The noise-free total-field anomalies produced by the synthetic sources at $z = −1, \300$ m 
(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = −1, \, 300$ m.

>>>>

The  three rows in Figure \ref{fig:synthetic_data_comparison_v2} show the flight patterns of the simulated airborne magnetic surveys (the upper row), the noise-corrupted total-field anomalies (the middle row) calculated over the flight patterns, and the true upward-continued total-field anomalies at $z = -1, \, 300$ m (the lower row).

@@

We performed the upward continuations of the noise-corrupted total-field anomalies 
(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method (equation \ref{eq:estimated-p-parameter-space}), 
the convolutional equivalent layer (our method), and 
the classical approach in the Fourier domain.
The noise-free total-field anomalies produced by the synthetic sources at $z = -1, \, 300$ m 
(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
